Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-22 article/article.tex
Commit 2024-05-22 04:15

\ldots\ldots\ldots\ldots.

These selections have some subjectivity, as the definition of clear sky,
is depended on the intended usage. Our main focus is to be able to
identify the OIR created by the clouds. Although, the aerosols and water
vapor are always present and can not be completely removed. The effect
of the different clearness levels

\ldots\ldots\ldots\ldots.

Another aspect of the CE events, that is often reported in the relative
bibliography, are cases of extreme cloud enhancement (ECE). These are
cases of CE where the measured intensity of the irradiance, exceeds the
equivalent TSI on the top of the atmosphere, and satisfy the
Equation\nobreakspace{}\ref{eq:ECE}. \begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
the solar constant, \(r\) the Sun -- Earth distance, and \(i\) each of
the one-minute observation.

>>>>

The definition of the CE events with this method, has a level of
subjectivity. The actual clear sky irradiance, is not known, and can
only be approximated. Although, because our main focus is to be able to
identify the OIR created by the clouds, we expect that we were able to
detect all the major events of OIR due to CE. Where, minor enhancements
may be not detected, are less significant for most of our results.

Another aspect of the CE events, that is often reported in the relative
bibliography, are cases of extreme cloud enhancement (ECE). These are
cases of CE, where the measured intensity of the irradiance, exceeds the
equivalent TSI on the top of the atmosphere, and satisfy the
Equation\nobreakspace{}\ref{eq:ECE}. \begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
the solar constant, \(r\) the Sun -- Earth distance, and \(i\) each of
the one-minute observation.

To give a better understanding of the CE identification procedure, we
included an example of the CE identification for a selected day \ldots.
appendix\ldots. where the use of the reference and the threshold are
shown, along with the relevant measurements.

Similar we provide yearly plots
